Flowchart of Current Algorithm

### 2008-11-11 docs/flowchart/flowchart.tex
not about time-centering p0 updated
added thermal conduction term into S
some temperature notes clarifications

\item At the beginning of each time step, we need an estimate for the time-centered
source term in the velocity divergence constraint,
\begin{equation}
  S =  -\sigma  \sum_k  \xi_k \omegadot_k  + 
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  {\omegadot}_k  + \sigma \Hnuc + \sigma \Hext \enskip ,
\label{eq:defineS} 
\end{equation}
(paper III; eq.~[19]).

@@

\MarginPar{is it really $p_0^n$ here and not $p_0^{\nph}$?}
\end{description}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1,\star} =  -\sigma  \sum_k  \xi_k  (\omegadot_k)^{(2),\star}  + 
  \sigma \Hnuc^{(2),\star} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2),\star}  
  + \sigma \Hext \enskip .
\end{equation} 
where $(\omegadot_k)^{(2),\star} = (\rho \omegadot_k)^{(2),\star} / \rho^{(2),\star}$
and the remaining quantities are defined using $X_k^{n+1,\star},$ $\rho^{n+1,\star},$ 
and $T^{n+1,\star}$ from step 5.
Then define
\begin{equation}
 S^\nph = \frac{S^n + S^{n+1,\star}}{2} \enskip. 
\end{equation}

@@

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is
\begin{equation}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) =
\beta_0^{\nph,\star}\left\{\left(S^{\nph} - \overline{S}^{\nph}\right)
 + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}
\left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)}^{\nph,\star}}{\Delta t^n}\right]\right\} \enskip ,
\end{equation}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1} =  -\sigma  \sum_k  \xi_k (\omegadot_k)^{(2)}  + \sigma \Hnuc^{(2)} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2)}  
   + \sigma \Hext \enskip ,
\end{equation}
where $(\omegadot_k)^{(2)} = (\rho \omegadot_k)^{(2)} / \rho^{(2)}$
and the remaining quantities are defined using $X_k^{n+1},$ $\rho^{n+1},$
and $T^{n+1}$ from step 9.

>>>>

\item At the beginning of each time step, we need an estimate for the time-centered
source term in the velocity divergence constraint,
\begin{equation}
  S =  -\sigma  \sum_k  \xi_k \omegadot_k  + 
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  {\omegadot}_k  + \sigma \Hnuc + \sigma \Hext 
  + \frac{\sigma}{\rho}\nabla\cdot\kth\nabla T \enskip ,
\label{eq:defineS} 
\end{equation}
(paper III; eq.~[19]).

@@

\MarginPar{We could time-center $p_0$ now that we have split out {\tt advect\_base\_pres}}
\end{description}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1,\star} =  -\sigma  \sum_k  \xi_k  (\omegadot_k)^{(2),\star}  + 
  \sigma \Hnuc^{(2),\star} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2),\star}  
  + \sigma \Hext + \frac{\sigma}{\rho}\nabla\cdot\kth\nabla T^{n+1,\star} \enskip .
\end{equation} 
where $(\omegadot_k)^{(2),\star} = (\rho \omegadot_k)^{(2),\star} / \rho^{(2),\star}$
and the thermodynamic quantities are defined using $\rho^{n+1,\star}, X_k^{n+1,\star},$ 
and $T^{n+1,\star}$ as inputs to the equation of state.
Then define
\begin{equation}
 S^\nph = \frac{S^n + S^{n+1,\star}}{2} \enskip. 
\end{equation}

@@

The procedure to construct $\uadvtwo$ is described in detail in Appendix B of paper III
and is analogous to the procedure used in step 2, but with updated values
for $w_0$ and $\pizero.$  We note that $\uadvtwo$ satisfies the discrete versions of 
equations (\ref{eq:udoterzero}) and (\ref{eq:tildeconstraint}).   The discretization
with the volume discrepancy correction is
\begin{eqnarray}
\nablab \cdotb \left(\beta_0^{\nph,\star} \uadvtwo\right) &=&
\beta_0^{\nph,\star}\left\{\left(S^{\nph} - \overline{S}^{\nph}\right)
 + \frac{f}{\gammabar^{\nph,\star} p_0^{\nph,\star}}\cdot \right. \nonumber \\
&& \left.\left[\frac{p(\rho,h,X_k)^{\nph,\star} - \overline{p(\rho,h,X_k)}^{\nph,\star}}{\Delta t^n}\right]\right\} \enskip ,
\end{eqnarray}
\begin{equation}
\beta_0^{\nph,\star} = \frac{ \beta_0^n +  \beta_0^{n+1,\star} }{2} \enskip .
\end{equation}

@@

\begin{enumerate}
\renewcommand{\theenumi}{{\bf \alph{enumi}}}
\item Define
\begin{equation}
  S^{n+1} =  -\sigma  \sum_k  \xi_k (\omegadot_k)^{(2)}  + \sigma \Hnuc^{(2)} +
  \frac{1}{\rho p_\rho} \sum_k p_{X_k}  ({\omegadot}_k)^{(2)}  
   + \sigma \Hext + \frac{\sigma}{\rho}\nabla\cdot\kth\nabla T^{n+1} \enskip ,
\end{equation}
where $(\omegadot_k)^{(2)} = (\rho \omegadot_k)^{(2)} / \rho^{(2)}$
and the thermodynamic quantities are defined using $\rho^{n+1}, X_k^{n+1},$
and $T^{n+1}$ as inputs to the equation of state.
